Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-14 Manuscript/manuscript.tex
Corrected wrong bracket.

In conclusion, the results suggest that calcium ions bind specifically to phosphate oxygens, occasionally interacting also with carbonyls. This is in good agreement with previous conclusions from several experimental and computational studies~\cite{hauser76, hauser78, herbette84, cevc90, binder02}, but suggesting a lower relative binding affinity to the carbonyls than inferred from previous MD simulation studies~\cite{bockmann03, bockmann04, melcrova16, javanainen17}. Sodium ions also interact primarily with phosphate oxygens of the POPC, but in contrast to calcium, the interactions purely with carbonyls are also significant. \todo{This last sentence is weak and not relevant. If you want to keep it go ahead, but then I would ask you a simple question: Is it incompatible to have no overall binding (this relates to the whole surface volume} with having small cavities in the membrane with an increase Na+ concentration. If the answer is negative maybe the statement is incorrect and who knows it might be relevant for something. After all even Ca2+ affinity changes in the presence of sodium.} The physiological relevance of these details of sodium interactions is, however, unclear due to its overall very weak binding affinity.

>>>>

In conclusion, the results suggest that calcium ions bind specifically to phosphate oxygens, occasionally interacting also with carbonyls. This is in good agreement with previous conclusions from several experimental and computational studies~\cite{hauser76, hauser78, herbette84, cevc90, binder02}, but suggesting a lower relative binding affinity to the carbonyls than inferred from previous MD simulation studies~\cite{bockmann03, bockmann04, melcrova16, javanainen17}. Sodium ions also interact primarily with phosphate oxygens of the POPC, but in contrast to calcium, the interactions purely with carbonyls are also significant. \todo{This last sentence is weak and not relevant. If you want to keep it go ahead, but then I would ask you a simple question: Is it incompatible to have no overall binding (this relates to the whole surface volume) with having small cavities in the membrane with an increase Na+ concentration. If the answer is negative maybe the statement is incorrect and who knows it might be relevant for something. After all even Ca2+ affinity changes in the presence of sodium.} The physiological relevance of these details of sodium interactions is, however, unclear due to its overall very weak binding affinity.
